Twisted \(M\)-theory and its perturbative quantization.

### 2020-11-04 paper.tex
merge
changes

The space of differential forms on any smooth manifold $L$ is a commutative dg algebra $\Omega^{\bu}(L) = \left(\oplus_{k}\Omega^{k}(L)[-k], \d_{\dR}\right)$.
By taking the tensor product with the dg Lie algebra $\cS(X)$ we obtain the dg Lie algebra
\beqn\label{localLie}
  \cS(X) \; \Hat{\otimes} \; \Omega^{\bu}(L)
\eeqn
where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
We remark that the structure maps of this Lie algebra, namely the differential and bracket, are given by differential and bidifferential operators, respectively.
In this sense, it fits the definition of a {\em local dg Lie algebra} on the product manifold $X \times L$, see Definition ?? \ref{CG2}.

Associated to any local dg Lie algebra is a classical field theory in the BV formalism that one refers to as ``$BF$-theory''.
Denote the sheaf of sections of the local dg Lie algebra by $\cL$.
The fields of the associated BV theory are pairs
\[
(A, B) \in \cL[1] \oplus \cL^{!}[-1]\]
and the action functional reads $\int B F_{A} = \int B (\d_{\cL}A + \frac12 [A,A])$.
Here $\d_{\cL}$ denotes the differential on $\cL$ and $[\cdot,\cdot]$ is the Lie bracket.
Notice that the equations of motion for the $A$-field is simply the Maurer--Cartan equation $\d_\cL A + \frac12 [A,A] = 0$.
For the $B$-field the equations of motion read $\d_\cL B + [A, B] = 0$.

@@

\begin{dfn}
Let $X$ be a Calabi--Yau five-fold and $L$ a one-dimensional smooth manifold.
Define the $\ZZ/2$-graded BV theory $\cT$ on
      \[
        X \times L
      \]
to be the deformation of BF theory for the $\ZZ/2$-graded local Lie algebra $\cS^{\leq 1,\bu}(X) \Hat{\otimes} \Omega^{\bu}(L)$ by the local functional

@@

There is a similar deformation of BF theory for the dg Lie algebra $\cS(X) \otimes \Omega^\bu(L)$ when $X$ is any {\em odd dimensional} Calabi--Yau manifold and $L$ is a smooth one-dimensional manifold.

@@

@@

>>>>

The space of differential forms on any smooth manifold $L$ is a commutative dg algebra $\Omega^{\bu}(L) = \left(\oplus_{k}\Omega^{k}(L)[-k], \d_{\dR}\right)$.
By taking the tensor product with the dg Lie algebra $\cS(X)$ we obtain the dg Lie algebra
\beqn\label{localLie}
  \cS(X) \; \Hat{\otimes} \; \Omega^{\bu}(L)
\eeqn
where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
The differential in this dg Lie algebra is of the form $\dbar \otimes 1 + \partial_\Omega \otimes 1 + 1 \otimes \d_{\rm dR}$, which we will abbreviate by $\dbar + \partial_\Omega + \d_{\rm dR}$.
The bracket is defined using the bracket on $\cS(X)$ together with the wedge product of forms on $\Omega^\bu(L)$ by the formula
\[
  [\mu \otimes \alpha, \nu \otimes \beta] = [\mu, \nu] \otimes (\alpha \wedge \beta) .
\]

We remark that the structure maps of this Lie algebra, namely the differential and bracket, are given by differential and bidifferential operators, respectively.
In this sense, it fits the definition of a {\em local dg Lie algebra} on the product manifold $X \times L$, see Definition ?? \ref{CG2}.

Associated to any local dg Lie algebra is a classical field theory in the BV formalism that one refers to as ``$BF$-theory''.
Denote the sheaf of sections of the local dg Lie algebra by $\cL$.
The fields of the associated BV theory are pairs
\[
  (A, B) \in \cL[1] \oplus \cL^{!}[-2]
\]
and the action functional reads $\int B F_{A} = \int B (\d_{\cL}A + \frac12 [A,A])$.
Here $\d_{\cL}$ denotes the differential on $\cL$ and $[\cdot,\cdot]$ is the Lie bracket.
Notice that the equations of motion for the $A$-field is simply the Maurer--Cartan equation $\d_\cL A + \frac12 [A,A] = 0$.
For the $B$-field the equations of motion read $\d_\cL B + [A, B] = 0$.

@@

\begin{dfn}
Let $X$ be a Calabi--Yau five-fold and $L$ a one-dimensional smooth manifold.
Define the $\ZZ/2$-graded BV theory $\cT$ on
      \[
        X \times L
      \]
to be the deformation of BF theory for the $\ZZ/2$-graded local Lie algebra $\cS(X) \Hat{\otimes} \Omega^{\bu}(L)$ by the local functional

@@

\subsubsection{}

We briefly discuss a generalization of this deformation of BF theory for the dg Lie algebra $\cS(X) \otimes \Omega^\bu(L)$ when $X$ is any {\em odd dimensional} Calabi--Yau manifold of dimension at least three and $L$ is a smooth one-dimensional manifold.

Suppose $X$ is a Calabi--Yau manifold of complex dimension $2m+1$ where $m > 0$.
Then, the fields of BF theory for the dg Lie algebra $\cS(X) \otimes \Omega^{\bu}(L)$ are of the form
\[
  \begin{array}{ccl}
    \mu = \mu^{1,\bu}+\mu^{0,\bu} & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
    \gamma = \gamma^{0,\bu} + \gamma^{1,\bu} & \in & \left(\Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X)[-1] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[depends on m] .
  \end{array}
\]

The deformation we consider is of the form
\[
  J_m (\gamma) = \int_{X \times L} \gamma \underbrace{\partial \gamma \cdots \partial \gamma}_{m} .
\]
That is, this deformation is $(m+1)$-linear and contains $m$ holomorphic derivatives.
As in the $m=2$ ($X$ is a five-fold) case that we discussed above, we see that $J_m$ is closed for the differential $\{S_{\rm BF},\cdot\}$ defining the BF theory.

\begin{lem}
  The functional $J_m$ is closed for the differential $\{S_{\rm BF}, \cdot \}$.
\end{lem}

A simple count reveals that the ghost degree of the functional $J_m$ is $depends on m$.
In particular, when $m \ne 1$, the above lemma implies that the action functional $S_{\rm BF} + J_m$ defines a $\ZZ/2$-graded classical BV theory.

When $m=1$, the action $S_{\rm BF} + J_1$ actually defines a $\ZZ$-graded BV theory.
Another feature of the case $m=1$ is that the deformed theory is actually a {\em topological} field theory.
It will be useful to spell out this theory in more detail.

In this case $X$ is a Calabi--Yau three-fold.
Using the isomorphism
\[
 (-) \vee \Omega : \PV^{i,\bu} (X) \cong \Omega^{3-i, \bu}(X)
\]
we can identify the $\mu$-fields of the theory in terms of differential forms
\[
  \alpha^2 + \alpha^3 \in \left(\Omega^{2,\bu}(X)[1] \oplus \Omega^{3,\bu}(X)\right) \; \Hat{\otimes} \; \Omega^\bu(L)
\]
by the formula $\alpha^{3-i} = \mu^{i} \vee \Omega$, for $i=0,1$.
We will also write $\alpha^{j} = \gamma^{j}$ for $j=0,1$, so the remaining fields are
\[
  \alpha^0 + \alpha^1 \in \left(\Omega^{0,\bu}(X)[3] \oplus \Omega^{1,\bu}(X)[2] \right) \; \Hat{\otimes} \; \Omega^\bu(L).
\]

Let us write the theory as $S_{\rm BF} + c J_1$ where $c$ is a complex number.
We denote by $\cT_c [X \times L]$ the resulting BV theory which depends on this coupling constant $c$.
Also, let $\cM_c[X]$ denote the moduli space of solutions on the Calabi--Yau three-fold $X$.

Using this decomposition of the fields we can write the underlying {\em free} theory by the following action functional
\[
  \int_{X\times L} \left(\alpha^0 (\dbar + \d_{\rm dR}) \alpha^3 + \alpha^1 (\dbar + \d_{\rm dR}) \alpha^2 \right) + \int_{X \times L} \alpha^0 \partial \alpha^2 + c \int_{X \times L} \alpha^1 \partial \alpha^1 .
\]
Here, as above, $\partial$ denotes the holomorphic de Rham operator on $X$.

Now, for $c \ne 0$, we observe that this free action is equivalent to abelian seven-dimensional Chern--Simons theory on $X \times L$.
Indeed, by the above formula the linear BRST complex of the theory is given by the following cochain complex
\[
  \bigg(\Omega^{\bu, \bu} (X) \; \Hat{\otimes} \; \Omega^{\bu}(L) [3] \; , \; \dbar + \Hat{\partial} + \d_{\rm dR} + c \partial_{\Omega^{1} \to \Omega^{2}} \bigg)
\]
Here, $\Hat{\partial}$ denotes the components of the holomorphic de Rham differential mapping $\Omega^{0,\bu}(X) \to \Omega^{1,\bu}(X)$ and $\Omega^{2,\bu}(X) \to \Omega^{3,\bu}(X)$, and $\partial_{\Omega^1 \to \Omega^2}$ denotes the component $\Omega^{1,\bu}(X) \to \Omega^{2,\bu}(X)$.
When $c \ne 0$ we see that this cochain complex is isomorphic to the full (shifted) de Rham complex $\Omega^\bu(X \times L)[3]$.

In the BV formalism, seven-dimensional Chern--Simons theory is described by the fields $\alpha^i \in \Omega^{i,\bu}(X) \Hat{\otimes} \Omega^\bu(L)[3-i]$, $i=0, \ldots 3$ which we can now decompose as a de Rham type field $C^\bu \in \Omega^\bu(X \times L)[3]$ so that $C^j$ has total de Rham degree $j$.
The BV antipairing is the wedge and integrate pairing $\int C \wedge C'$ and the action reads
\[
  \frac{1}{2} \int_{X \times L} C \d C,
\]
where $\d$ is the full de Rham differential on $X \times L$.
Sometimes, this is referred to as ``three-form Chern--Simons theory'' since its fundamental field is a three-form $C^3$ and the equations of motion read $\d C^3 = 0$.

We have seen that when $c \ne 0$, the free theory underlying $\cT_c[X \times L]$ is equivalent to seven-dimensional Chern--Simons theory.
In particular, the moduli space of solutions $\cM_c[X]$, for $c \ne 0$, has as its free limit the moduli space of circle $3$-bundles on $X$ with connection.

We can consider a different limit of $\cM_c[X]$, namely the one where $c \to 0$.
This is precisely the cotangent bundle to the moduli space of Calabi--Yau structures $\cM_{CY}[X]$ on the three-fold $X$:
\[
  \cM_0[X] = T^* \left(\cM_{\rm CY} [X]\right) .
\]

In summary, we have seen that $\cM_c[X]$ provides a roof of deformations between the moduli space of Calabi--Yau structures on $X$ and the moduli of circle $3$-bundles:
\[
  \begin{tikzcd}
    & \cM_c[X] \ar[dr, "c \ne 0"', "{\rm free\;limit}"] \ar[dl, "c \to 0"'] & \\ T^* \left(\cM_{\rm CY} [X] \right) & & \left\{ \begin{array}{ccc} \mbox{circle\;3-bundles} \\ {\rm on} \; X \end{array} \right\} .
  \end{tikzcd}
\]

@@

\brian{state conjecture about twist.}

@@

We recall that our eleven-dimensional theory is only $\ZZ/2$-graded.
This is consistent with the minimal twist of supergravity.
Indeed, since the $R$-symmetry group is trivial there is no way to regrade the twisted theory in such a way that the BRST differential and twisting supercharge are of homogenous $\ZZ$-degree.

The conjecture implies that the even fields of our eleven dimensional theory should correspond to certain components of the fundamental fields supergravity that survive the minimal twist.
The even components of the field $\mu$ and $\gamma$ are of the form
\[
  \mu^{0, i ; j} \; , \; \mu^{1, i ; j} \; , \; \gamma^{0, i ; j} \; , \; \gamma^{1, i ; j}
\]
where $i+j$ is an even integer and $i = 0,\ldots 5$ and $j=0,1$.
Here, as in the previous section, we have used the following index notation:
\[
  \begin{array}{ccccc}
    \mu^{k, i ; j} & \in & \pv^{k,i} (\CC^5) \; \Hat{\otimes} \; \Omega^j(\RR) \\
    \gamma^{k, i ; j} & \in & \Omega^{k,i}(\CC^5) \; \Hat{\otimes} \; \Omega^j(\RR).
  \end{array}
\]

Let us now turn to the field content of eleven-dimensional supergravity.
In Euclidean signature, in the flat background, the fundamental fields of eleven-dimensional supergravity are
\[
  \begin{array}{ccll}
    e & \in & \Omega^1(\RR^{11}) \otimes \CC^{11} & \mbox{vielbien} \\
    \omega & \in & \Omega^1(\RR^{11}) \otimes \fs \fo(11) & \mbox{spin connection} \\
    C & \in & \Omega^3(\RR^{11}) & \mbox{supergravity $3$-form} \\
    \psi & \in & \Omega^1(\RR^{11}) \otimes S & \mbox{gravitino} .
  \end{array}
\]
We note that the fields above have been complexified from the usual presentation of supergravity in terms of real fields.
Here, $S$ denotes the $128$ dimensional complex spin representation of $\fs \fo(11)$.
